\section{Discussion and Limitations}

Baihu provides a large-scale, standardized, and temporally structured data foundation for embodied intelligence research. Its main strengths lie in its scale, fully human-teleoperated collection protocol, multi-platform coverage, preservation of platform-specific observation and action schemas, conversion into the LeRobot v2.1 format, and event/keyframe-level temporal annotations. With \textbf{9521.75 hours}, \textbf{513575 episodes}, and more than \textbf{1.03 billion frames} of robot data, Baihu supports foundation-model adaptation regimes that are difficult to study using smaller task-specific datasets.

The offline zero-shot benchmark provides initial evidence that Baihu is useful for embodied foundation model adaptation. The evaluation datasets are external to Baihu and are excluded from Baihu training. Across 13 platforms and 42 paired task-dataset records, the GR00T N1.6 checkpoint fully fine-tuned on Baihu substantially reduces both Normalized ALL MSE and Normalized Joint MSE compared with the no-training checkpoint. Each task-level result is averaged over five evaluation trajectories, and both checkpoints are evaluated on the same trajectories. These results suggest that Baihu fine-tuning transfers effectively to separately collected robot demonstration data.

Baihu's event/keyframe annotations provide a second capability beyond dense action supervision. They expose task progress and semantic milestones that are often hidden in raw observation-action trajectories. This makes Baihu compatible with keyframe-aware learning paradigms such as waypoint-conditioned imitation learning, goal-conditioned policy learning, hierarchical skill decomposition, reward shaping, value-guided policy improvement, subgoal-image reasoning, and phase-aware evaluation. The annotations should therefore be interpreted as a general temporal structure resource rather than as labels designed only for a single reinforcement-learning algorithm.

At the same time, the current benchmark should be interpreted as an offline action-prediction evaluation rather than a complete measure of real-world robot performance. Open-loop normalized MSE measures agreement with reference teleoperation actions, but it does not capture closed-loop recovery, contact-rich interaction, or task success under real robot execution. In sequential decision making, prediction errors can alter future observations and compound under the policy-induced state distribution~\cite{ross2011dagger,zhao2023aloha}. Moreover, the benchmark demonstrates dataset-level transfer because the evaluation datasets are external to Baihu, but it should not be interpreted as a held-out-platform experiment when the evaluated robot platform is also represented in Baihu.

Another limitation is that the current paper focuses on a single completed benchmark setting: a GR00T N1.6 checkpoint comparison under offline open-loop evaluation. Additional baselines such as ACT, Behavior Transformer, Diffusion Policy, or open-source vision-language-action policies would make the benchmark more comprehensive~\cite{zhao2023aloha,shafiullah2022behaviortransformer,chi2023diffusionpolicy,kim2024openvla}. Data-scaling experiments, held-out-platform evaluation, and closed-loop robot rollouts would further clarify which aspects of Baihu contribute most to model performance. The current benchmark also uses an unweighted mean across task-dataset records; future work could additionally report trajectory-weighted results and uncertainty estimates across evaluation trajectories.

Finally, although Baihu provides event- and keyframe-level annotations, the current paper has not yet completed the planned real-world evaluation of event-guided value learning. Therefore, the event/keyframe annotations should be treated in this version as a dataset capability and reserved experimental direction, not as a fully validated claim that these annotations already improve real-world execution success rate. Future versions will compare policies trained with and without event-derived value supervision on real robot tasks, reporting execution success rate, event completion rate, failure stage distribution, and time to completion.
