\section{Conclusion}

We introduced \textbf{Whitetiger}, a billion-frame, fully human-teleoperated, multi-platform robot manipulation dataset for embodied foundation model adaptation and event-aware robot learning. Whitetiger contains \textbf{9521.75 hours} of robot data, \textbf{2989 tasks}, \textbf{513575 episodes}, and \textbf{1028349814 frames} across \textbf{13 robot platforms}. The dataset converts platform-specific HDF5 robot operation records into the LeRobot v2.1 format, providing a standardized data foundation for training vision-language-action models and generalist robot policies.

Whitetiger combines two complementary dataset properties: scale and temporal structure. Its large-scale dense trajectories support foundation-model adaptation and offline zero-shot action prediction on datasets external to Whitetiger. Its event- and keyframe-level temporal annotations expose task progress and semantic milestones beyond gripper or dexterous-hand state changes. These annotations make Whitetiger compatible with keyframe-aware learning paradigms such as waypoint-conditioned imitation learning, goal-conditioned policy learning, hierarchical skill decomposition, reward shaping, value-guided policy improvement, subgoal-image reasoning, and phase-aware evaluation.

We evaluated the utility of Whitetiger through offline open-loop zero-shot evaluation on external datasets excluded from Whitetiger training. Across 13 platforms and 42 paired task-dataset records, a GR00T N1.6 model trained on Whitetiger for one epoch reduced \textbf{Normalized ALL MSE by 96.79\%} and \textbf{Normalized Joint MSE by 99.42\%} compared with the no-training baseline. Each task-level result was averaged over five evaluation trajectories. These results suggest that Whitetiger provides effective large-scale supervision for robot action prediction and can serve as practical infrastructure for future embodied foundation model development.

Future work will extend Whitetiger with additional benchmark protocols, more baseline models, closed-loop evaluations, data-scaling studies, held-out-platform evaluation, and clearer release documentation. A planned real-world comparison between dense trajectory training and event-derived value supervision will evaluate whether Whitetiger temporal annotations improve real-robot execution success rate. Together, these directions can further strengthen Whitetiger as a reusable data foundation for large-scale and temporally structured embodied intelligence research.
